---
title: "Mental health outcomes DataSchema"
output: html_document
---
# Table of Contents
1. [Anxiety subdomain](#anxiety-subdomain)
2. [Cognitive functioning subdomain](#cognitive-functioning-subdomain)
3. [Depression subdomain](#depression-subdomain) 
4. [Life satisfaction subdomain](#life-satisfaction-subdomain)
5. [Loneliness subdomain](#loneliness-subdomain)
6. [Post-traumatic stress subdomain](#post-traumatic-stress-subdomain)
7. [Psychological distress subdomain](#psychological-distress-subdomain)
8. [Quality of life subdomain](#quality-of-life-subdomain)

# Anxiety subdomain

### **Variable label**:  Anxiety symptom score measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A) 
**Variable name**:   psy_anxiety_score_0  
**Variable description**:  Anxiety symptom score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Anxiety symptom score measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)  
**Variable name**:   psy_anxiety_score_1  
**Variable description**:  Anxiety symptom score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:     
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Anxiety symptom score measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)   
**Variable name**:   psy_anxiety_score_2  
**Variable description**:  Anxiety symptom score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Anxiety symptom score measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A) 
**Variable name**:   psy_anxiety_score_3  
**Variable description**:  Anxiety symptom score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:    
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Anxiety symptom score measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)   
**Variable name**:   psy_anxiety_score_4  
**Variable description**:  Anxiety symptom score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Anxiety symptom score measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)   
**Variable name**:   psy_anxiety_score_5  
**Variable description**:  Anxiety symptom score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Anxiety symptom score measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)   
**Variable name**:   psy_anxiety_score_6  
**Variable description**:  Anxiety symptom score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Caseness of anxiety measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)
**Variable name**:   psy_anxiety_case_0  
**Variable description**:  Indicator of whether the participant has elevated anxiety symptoms in accordance with the HADS-A threshold from Zigmond & Snaith (1983) and Snaith (2003).    
**Value type**:  integer      
**Variable unit**:  N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (0-10 anxiety symptom score)
1 |   Case (11-21 anxiety symptom score)

**Harmonization status**:  
**Harmonization comment**:      
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Caseness of anxiety measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)
**Variable name**:   psy_anxiety_case_1  
**Variable description**:  Indicator of whether the participant has elevated anxiety symptoms in accordance with the HADS-A threshold from Zigmond & Snaith (1983) and Snaith (2003).    
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (0-10 anxiety symptom score)
1 |   Case (11-21 anxiety symptom score)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Caseness of anxiety measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A) 
**Variable name**:   psy_anxiety_case_2  
**Variable description**:  Indicator of whether the participant has elevated anxiety symptoms in accordance with the HADS-A threshold from Zigmond & Snaith (1983) and Snaith (2003).    
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (0-10 anxiety symptom score)
1 |   Case (11-21 anxiety symptom score)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Caseness of anxiety measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)  
**Variable name**:   psy_anxiety_case_3  
**Variable description**:  Indicator of whether the participant has elevated anxiety symptoms in accordance with the HADS-A threshold from Zigmond & Snaith (1983) and Snaith (2003).   
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (0-10 anxiety symptom score)
1 |   Case (11-21 anxiety symptom score)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Caseness of anxiety measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)  
**Variable name**:   psy_anxiety_case_4  
**Variable description**:  Indicator of whether the participant has elevated anxiety symptoms in accordance with the HADS-A threshold from Zigmond & Snaith (1983) and Snaith (2003).    
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (0-10 anxiety symptom score)
1 |   Case (11-21 anxiety symptom score)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Caseness of anxiety measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)  
**Variable name**:   psy_anxiety_case_5  
**Variable description**:  Indicator of whether the participant has elevated anxiety symptoms in accordance with the HADS-A threshold from Zigmond & Snaith (1983) and Snaith (2003).   
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (0-10 anxiety symptom score)
1 |   Case (11-21 anxiety symptom score)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Caseness of anxiety measured by the Hospital Anxiety & Depression Scale - Anxiety subscale (HADS-A)  
**Variable name**:   psy_anxiety_case_6  
**Variable description**:  Indicator of whether the participant has elevated anxiety symptoms in accordance with the HADS-A threshold from Zigmond & Snaith (1983) and Snaith (2003).     
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:    

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (0-10 anxiety symptom score)
1 |   Case (11-21 anxiety symptom score)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Feels anxious or nervous  
**Variable name**:   psy_anxious_yn_0  
**Variable description**:  Single item question on whether the participant feels anxious or nervous.  
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel anxious or nervous
1 |   Feels anxious or nervous

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Feels anxious or nervous  
**Variable name**:   psy_anxious_yn_1  
**Variable description**:  Single item question on whether the participant feels anxious or nervous.  
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel anxious or nervous
1 |   Feels anxious or nervous

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Feels anxious or nervous  
**Variable name**:   psy_anxious_yn_2  
**Variable description**:  Single item question on whether the participant feels anxious or nervous.  
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel anxious or nervous
1 |   Feels anxious or nervous

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Feels anxious or nervous  
**Variable name**:   psy_anxious_yn_3  
**Variable description**:  Single item question on whether the participant feels anxious or nervous.  
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel anxious or nervous
1 |   Feels anxious or nervous

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Feels anxious or nervous  
**Variable name**:   psy_anxious_yn_4  
**Variable description**:  Single item question on whether the participant feels anxious or nervous.  
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel anxious or nervous
1 |   Feels anxious or nervous

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Feels anxious or nervous  
**Variable name**:   psy_anxious_yn_5  
**Variable description**:  Single item question on whether the participant feels anxious or nervous.  
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel anxious or nervous
1 |   Feels anxious or nervous

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   Feels anxious or nervous  
**Variable name**:   psy_anxious_yn_6  
**Variable description**:  Single item question on whether the participant feels anxious or nervous.  
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel anxious or nervous
1 |   Feels anxious or nervous

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Cognitive functioning subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Depression subdomain

### **Variable label**:  Depressive symptom severity tertile    
**Variable name**:  psy_depression_tertile_0  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of depressive symptoms measured by scale-specific depressive symptom score.     
**Value type**:  integer   
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Low severity tertile of depressive symptoms
1 |   Medium severity tertile of depressive symptoms
2 |   High severity tertile of depressive symptoms 

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Depressive symptom severity tertile  
**Variable name**:  psy_depression_tertile_1    
**Variable description**:  Indicator of whether the participants has low, medium or high severity of depressive symptoms measured by scale-specific depressive symptom score.    
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Low severity tertile of depressive symptoms
1 |   Medium severity tertile of depressive symptoms
2 |   High severity tertile of depressive symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Depressive symptom severity tertile      
**Variable name**:  psy_depression_tertile_2  
**Variable description**:  Indicator of whether the participants has low, medium or high severity of depressive symptoms measured by scale-specific depressive symptom score.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Low severity tertile of depressive symptoms
1 |   Medium severity tertile of depressive symptoms
2 |   High severity tertile of depressive symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Depressive symptom severity tertile    
**Variable name**:  psy_depression_tertile_3  
**Variable description**:  Indicator of whether the participants has low, medium or high severity of depressive symptoms measured by scale-specific depressive symptom score.      
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Low severity tertile of depressive symptoms
1 |   Medium severity tertile of depressive symptoms
2 |   High severity tertile of depressive symptoms    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Depressive symptom severity tertile    
**Variable name**:  psy_depression_tertile_4  
**Variable description**:  Indicator of whether the participants has low, medium or high severity of depressive symptoms measured by scale-specific depressive symptom score.      
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Low severity tertile of depressive symptoms
1 |   Medium severity tertile of depressive symptoms
2 |   High severity tertile of depressive symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Depressive symptom severity tertile      
**Variable name**:  psy_depression_tertile_5  
**Variable description**:  Indicator of whether the participants has low, medium or high severity of depressive symptoms measured by scale-specific depressive symptom score.    
**Value type**:  integer  
**Variable unit**:  N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Low severity tertile of depressive symptoms
1 |   Medium severity tertile of depressive symptoms
2 |   High severity tertile of depressive symptoms    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Depressive symptom severity tertile    
**Variable name**:  psy_depression_tertile_6  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of depressive symptoms measure by scale-specific depressive symptom score.   
**Value type**:  integer    
**Variable unit**:  N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Low severity tertile of depressive symptoms
1 |   Medium severity tertile of depressive symptoms
2 |   High severity tertile of depressive symptoms   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Caseness of depression      
**Variable name**:  psy_depression_case_0      
**Variable description**:  Indicator of whether the participant has elevated depressive symptoms in accordance with the scale-specific threshold of depressive symptom score.  
**Value type**:  integer     
**Variable unit**:  N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated depressive symptoms)  
1 |   Case (elevated depressive symptoms)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Caseness of depression    
**Variable name**:  psy_depression_case_1    
**Variable description**:  Indicator of whether the participant has elevated depressive symptoms in accordance with the scale-specific threshold of depressive symptom score.  
**Value type**:  integer    
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated depressive symptoms)  
1 |   Case (elevated depressive symptoms)  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Caseness of depression    
**Variable name**:  psy_depression_case_2  
**Variable description**:  Indicator of whether the participant has elevated depressive symptoms in accordance with the scale-specific threshold of depressive symptom score.  
**Value type**:  integer  
**Variable unit**:  N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated depressive symptoms)  
1 |   Case (elevated depressive symptoms)   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Caseness of depression  
**Variable name**:  psy_depression_case_3  
**Variable description**:  Indicator of whether the participant has elevated depressive symptoms in accordance with the scale-specific threshold of depressive symptom score.  
**Value type**:  integer  
**Variable unit**:  N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated depressive symptoms)  
1 |   Case (elevated depressive symptoms)   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Caseness of depression    
**Variable name**:  psy_depression_case_4  
**Variable description**:  Indicator of whether the participant has elevated depressive symptoms in accordance with the scale-specific threshold of depressive symptom score.  
**Value type**:  integer  
**Variable unit**:  N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated depressive symptoms)  
1 |   Case (elevated depressive symptoms)     

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Caseness of depression  
**Variable name**:  psy_depression_case_5    
**Variable description**:  Indicator of whether the participant has elevated depressive symptoms in accordance with the scale-specific threshold of depressive symptom score.  
**Value type**:  integer  
**Variable unit**:  N/A    
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated depressive symptoms)  
1 |   Case (elevated depressive symptoms)       

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Caseness of depression    
**Variable name**:  psy_depression_case_6  
**Variable description**:  Indicator of whether the participant has elevated depressive symptoms in accordance with the scale-specific threshold of depressive symptom score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated depressive symptoms)  
1 |   Case (elevated depressive symptoms)    

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Feels sad, downhearted or blue  
**Variable name**:  psy_depressed_yn_0  
**Variable description**:  Single item question on whether the participant feels sad, downhearted or blue.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel sad, downhearted or blue
1 |   Feels sad, downhearted or blue

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Feels sad, downhearted or blue  
**Variable name**:  psy_depressed_yn_1  
**Variable description**:  Single item question on whether the participant feels sad, downhearted or blue.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel sad, downhearted or blue
1 |   Feels sad, downhearted or blue

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Feels sad, downhearted or blue  
**Variable name**:  psy_depressed_yn_2  
**Variable description**:  Single item question on whether the participant feels sad, downhearted or blue.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel sad, downhearted or blue
1 |   Feels sad, downhearted or blue

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Feels sad, downhearted or blue  
**Variable name**:  psy_depressed_yn_3  
**Variable description**:  Single item question on whether the participant feels sad, downhearted or blue.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel sad, downhearted or blue
1 |   Feels sad, downhearted or blue

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Feels sad, downhearted or blue  
**Variable name**:  psy_depressed_yn_4  
**Variable description**:  Single item question on whether the participant feels sad, downhearted or blue.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel sad, downhearted or blue
1 |   Feels sad, downhearted or blue

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Feels sad, downhearted or blue  
**Variable name**:  psy_depressed_yn_5  
**Variable description**:  Single item question on whether the participant feels sad, downhearted or blue.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel sad, downhearted or blue
1 |   Feels sad, downhearted or blue

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Feels sad, downhearted or blue  
**Variable name**:  psy_depressed_yn_6  
**Variable description**:  Single item question on whether the participant feels sad, downhearted or blue.    
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Does not feel sad, downhearted or blue
1 |   Feels sad, downhearted or blue

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Life satisfaction subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Loneliness subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Post-traumatic stress subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Psychological distress subdomain

### **Variable label**:  Psychological distress severity tertile  
**Variable name**:  psy_distress_tertile_0  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of psychological distress symptoms measured by scale-specific psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Low severity tertile of psychological distress symptoms  
1 | Medium severity tertile of psychological distress symptoms  
2 | High severity tertile of psychological distress symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Psychological distress severity tertile  
**Variable name**:  psy_distress_tertile_1  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of psychological distress symptoms measured by scale-specific psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Low severity tertile of psychological distress symptoms  
1 | Medium severity tertile of psychological distress symptoms  
2 | High severity tertile of psychological distress symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Psychological distress severity tertile  
**Variable name**:  psy_distress_tertile_2  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of psychological distress symptoms measured by scale-specific psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Low severity tertile of psychological distress symptoms  
1 | Medium severity tertile of psychological distress symptoms  
2 | High severity tertile of psychological distress symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Psychological distress severity tertile  
**Variable name**:  psy_distress_tertile_3  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of psychological distress symptoms measured by scale-specific psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Low severity tertile of psychological distress symptoms  
1 | Medium severity tertile of psychological distress symptoms  
2 | High severity tertile of psychological distress symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Psychological distress severity tertile  
**Variable name**:  psy_distress_tertile_4  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of psychological distress symptoms measured by scale-specific psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Low severity tertile of psychological distress symptoms  
1 | Medium severity tertile of psychological distress symptoms  
2 | High severity tertile of psychological distress symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Psychological distress severity tertile  
**Variable name**:  psy_distress_tertile_5  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of psychological distress symptoms measured by scale-specific psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Low severity tertile of psychological distress symptoms  
1 | Medium severity tertile of psychological distress symptoms  
2 | High severity tertile of psychological distress symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
### **Variable label**:  Psychological distress severity tertile  
**Variable name**:  psy_distress_tertile_6  
**Variable description**:  Indicator of whether the participant has low, medium or high severity of psychological distress symptoms measured by scale-specific psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Low severity tertile of psychological distress symptoms  
1 | Medium severity tertile of psychological distress symptoms  
2 | High severity tertile of psychological distress symptoms  

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Caseness of psychological distress    
**Variable name**:  psy_distress_case_0      
**Variable description**:  Indicator of whether the participant has elevated psychological distress symptoms in accordance with the scale-specific threshold of psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated psychological distress symptoms)
1 |   Case (elevated psychological distress symptoms)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Caseness of psychological distress    
**Variable name**:  psy_distress_case_1        
**Variable description**:  Indicator of whether the participant has elevated psychological distress symptoms in accordance with the scale-specific threshold of psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated psychological distress symptoms)
1 |   Case (elevated psychological distress symptoms)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Caseness of psychological distress    
**Variable name**:  psy_distress_case_2      
**Variable description**:  Indicator of whether the participant has elevated psychological distress symptoms in accordance with the scale-specific threshold of psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated psychological distress symptoms)
1 |   Case (elevated psychological distress symptoms)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Caseness of psychological distress    
**Variable name**:  psy_distress_case_3      
**Variable description**:  Indicator of whether the participant has elevated psychological distress symptoms in accordance with the scale-specific threshold of psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated psychological distress symptoms)
1 |   Case (elevated psychological distress symptoms)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Caseness of psychological distress    
**Variable name**:  psy_distress_case_4      
**Variable description**:  Indicator of whether the participant has elevated psychological distress symptoms in accordance with the scale-specific threshold of psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated psychological distress symptoms)
1 |   Case (elevated psychological distress symptoms)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Caseness of psychological distress    
**Variable name**:  psy_distress_case_5      
**Variable description**:  Indicator of whether the participant has elevated psychological distress symptoms in accordance with the scale-specific threshold of psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated psychological distress symptoms)
1 |   Case (elevated psychological distress symptoms)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  Caseness of psychological distress    
**Variable name**:  psy_distress_case_6      
**Variable description**:  Indicator of whether the participant has elevated psychological distress symptoms in accordance with the scale-specific threshold of psychological distress score.  
**Value type**:  integer  
**Variable unit**:  N/A  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   Non-case (no elevated psychological distress symptoms)
1 |   Case (elevated psychological distress symptoms)

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Quality of life subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
