---
title: "Mental health outcomes DataSchema"
output: html_document
---
# Table of Contents
1. [Anxiety subdomain](#anxiety-subdomain)
2. [Cognitive functioning subdomain](#cognitive-functioning-subdomain)
3. [Depression subdomain](#depression-subdomain) 
4. [Life satisfaction subdomain](#life-satisfaction-subdomain)
5. [Loneliness subdomain](#loneliness-subdomain)
6. [Post-traumatic stress subdomain](#post-traumatic-stress-subdomain)
7. [Psychological distress subdomain](#psychological-distress-subdomain)
8. [Quality of life subdomain](#quality-of-life-subdomain)

# Anxiety subdomain

### **Variable label**:  anxiety symptoms score  
**Variable name**:   psy_anxiety_score_0  
**Variable description**:  Anxiety symptoms score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   Anxiety subscale from the Hospital Anxiety and Depression Scale (HADS).  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  anxiety symptoms score  
**Variable name**:   psy_anxiety_score_1  
**Variable description**:  Anxiety symptoms score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   Anxiety subscale from the Hospital Anxiety and Depression Scale (HADS).  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  anxiety symptoms score  
**Variable name**:   psy_anxiety_score_2  
**Variable description**:  Anxiety symptoms score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   Anxiety subscale from the Hospital Anxiety and Depression Scale (HADS).  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  anxiety symptoms score  
**Variable name**:   psy_anxiety_score_3  
**Variable description**:  Anxiety symptoms score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   Anxiety subscale from the Hospital Anxiety and Depression Scale (HADS).  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  anxiety symptoms score  
**Variable name**:   psy_anxiety_score_4  
**Variable description**:  Anxiety symptoms score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   Anxiety subscale from the Hospital Anxiety and Depression Scale (HADS).  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  anxiety symptoms score  
**Variable name**:   psy_anxiety_score_5  
**Variable description**:  Anxiety symptoms score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   Anxiety subscale from the Hospital Anxiety and Depression Scale (HADS).  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:  anxiety symptoms score  
**Variable name**:   psy_anxiety_score_6  
**Variable description**:  Anxiety symptoms score ranging from 0 to 21.  
**Value type**:  integer  
**Variable unit**:  score  
**Category coding**:  N/A  
 
**Harmonization status**:  
**Harmonization comment**:   Anxiety subscale from the Hospital Anxiety and Depression Scale (HADS).  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

### **Variable label**:   
**Variable name**:   
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```


# Cognitive functioning subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Depression subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Life satisfaction subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Loneliness subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Post-traumatic stress subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Psychological distress subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```

# Quality of life subdomain

### **Variable label**:  
**Variable name**:  
**Variable description**:  
**Value type**:  
**Variable unit**:  
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 |   
1 |   

**Harmonization status**:  
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```
